---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IMBEIstyle

<!-- badges: start -->
<!-- badges: end -->

The goal of IMBEIstyle is to provide a simple way to create an analysis report, styled
up with some fancy options and some UM corporate design colors, and a revealjs quarto
presentation, in a similar fashion.

More content could cover the need of e.g. a poster template - especially if doable 
within the quarto framework.

## Installation

You can install the development version of IMBEIstyle like so:

``` r
library("remotes")
remotes::install_github("imbeimainz/IMBEIstyle")
```

## Example

Here is how you can create the reports and presentations with this package

```{r example}
library("IMBEIstyle")

IMBEIstyle::create_bioinfo_html(file_name = "myfirstreport",
                                report_folder = tempdir())

IMBEIstyle::create_bioinfo_revealjs("myveryfirstpresentation",
                                    presentation_folder = tempdir())
```
